\documentclass[12pt,landscape]{article}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{csvsimple}
\usepackage{graphicx}
\usepackage{hyperref}
\parindent=0pt
\parskip=5 pt
\setlength{\textwidth=9in}
\setlength{\oddsidemargin=-.5 in}
\setlength{\topmargin=0 in}
\setlength{\textheight=7 in}
%\usepackage{draftwatermark}
%\SetWatermarkText{Draft}
%\SetWatermarkScale{5}
\title{DUNE Offline Computing Model Calculations for 2023 - Appendix with 2040 projections. }
\author{H. Schellman for the Computing Consortium}
\date{\today -- version 3.1}
\newcommand{\hrefII}[1]{\href{#1}{#1}}
\begin{document}


\makeatletter
\csvset{
  autotabularright/.style={
    file=#1,
    after head=\csv@pretable\begin{tabular}{|*{\csv@columncount}{r|}}\csv@tablehead,
    table head=\hline\csvlinetotablerow\\\hline,
    late after line=\\,
    table foot=\\\hline,
    late after last line=\csv@tablefoot\end{tabular}\csv@posttable,
    command=\csvlinetotablerow},
}
\makeatother
\newcommand{\csvautotabularright}[2][]{\footnotesize\csvloop{autotabularright={#2},#1}}

\maketitle
\input{bibmaker.tex}
\clearpage
\appendix

\clearpage
\section{Model Details}

This appendix shows the parameters used in the model and plots of all the input and derived quantities as a function of time. 

Resource needs for reconstructed data for a given year are based on the number of events produced over the previous "Reprocess" years.   For ProtoDUNEs that is 2-4 years. 

Simulation resource needs are instead calculated based on a number of simulation events each year. The assumption is that new software versions imply resimulation.

Disk and tape lifetimes for different data types are specified as well as the desirable number of copies. 

The splits parameters make CERN responsible for raw data until 2027 with the collaboration taking over after that point. 

\footnotesize

\input{MoreSim_2022-12-09-2040/tables.tex}
\end{document}

